### 2017-09-25 TF-vldb2018/sec-appendix.tex

\noindent
{\textbf{1. Procedure \rgraphsim (Section~\ref{subsec-teamF})}}

\vspace{-2ex}
\begin{figure}[h!]
%\vspace{-2ex}
\begin{center}
{\small
\myhrule
\vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} Pattern graph $P(V_{P}, E_{P})$, ball $\ball([v, r])$.\\
{\sl Output:\/} The perfect subgraph $G_s$ of $\ball{[v,r]}$ \wrt $P$.\\
\sstab \bcc \hspace{1ex} \= \For each $u \in V_{P}$ \Do\\
\icc \>\hspace{2ex}\= $\matchs(u)$ := \{$w | w$ is in $\ball{[v, r]}$ and $l_P(u)\in l(w)$\};\\
\icc \> \While there are changes \Do\\
\icc \>\> \For each edge ($u, u'$) in $E_P$ and each node $w \in \matchs(u)$ \Do\\
\icc \>\>\hspace{2ex}\= \If there is no edge ($w, w'$) in $\ball{[v, r]}$ with $w' \in \matchs(u')$ \Then\\
\icc \>\>\>\hspace{2ex}\= $\matchs(u)$ := $\matchs(u) \setminus \{w\}$;\\
\icc \> \If there exists $|\matchs(u)|\not\in f_{P}(u)$ \Then \Return $\emptyset$;\\
\icc \> $\Reps$ := \{$(u,w) | u \in V_{P}, w \in \matchs(u)$\};\\
\icc \> Construct the perfect subgraph $G_s$ \wrt $\Reps$;\\
\icc \> \Return $G_s$;\\
}

@@

\noindent
{\textbf{2. Algorithm \minp (Section~\ref{subsec-batch-opt})}}

@@

\vspace{-2ex}
\etitle{Correctness \& Complexity}. The correctness of \minp is assured by following.
(1) The maximum match relations returned by $P$ and $P_{m}$ on any data graph $G$ are always same via graph simulation.
(2) The generated capacity bound on each node in $P_{m}$ assures that, the matched nodes of $P_{m}$ in $G$ always satisfy all capacity bounds on the nodes in $P$, which are in the same equivalent class.
Till now, $P\equiv P_{m}$;
(3) For any $P'$ that $P'\equiv P_{m}$, $|P_{m}|\leq|P'|$.
Algorithm \minp is in $O(|P|^2)$ time, by the time complexity of graph simulation.

\noindent
{\textbf{3. Algorithm \kw{PFrag} (Section~\ref{subsec-framework})}}

Algorithm \kw{PFrag} works by connecting the {\em pattern fragmentation} problem to the
{\sc $(k, \nu)$-Balanced Partition} problem.
It is to divide the nodes of a graph into $k$ components such that each component is of size no more than $\nu\cdot\frac{|V|}{k}$, and the number of edges between different components is minimized.
As illustrated before, the $(k,\nu)$-balanced partition problem,
though is not approximable in general, has a number of sophisticated heuristic algorithms~\cite{AndreevR06}.

\vspace{-2ex}
\begin{figure}[h!]
\begin{center}
{\small
\begin{center}
\myhrule \vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} \= Pattern graph $P(V_{P},E_{P})$, integer $h$.\\
{\sl Output:\/} An $h$-fragmentation \{${P}_{f1}$, \ldots, ${P}_{fh}$, $C$\} of $P$.\\
\sstab \bcc \hspace{0.5ex} \= $k$ := $h$; $\nu$ := $h$; $M_P$ := $|P|$; $M_C$ := 0;\\
\icc \> $({P}^\nu_{f1}, \ldots, {P}^\nu_{fh}, C^\nu)$ := $\kw{BalanceP}(k,\nu)$; \\
\icc \> $M^\nu_P$ := $\kw{max}\{|{P}^\nu_{f1}|, \ldots, |{P}^\nu_{fh}|\}$; $M^\nu_C$ := $|C^\nu|$;\\
\icc\> \While $\kw{max}\{M_P, M_C\} > \kw{max}\{M^\nu_P, M^\nu_C\}$ \Do\\
\icc \>\hspace{2ex}\= ${P}_{f1}$ := ${P}^\nu_{f1}$, \ldots, ${P}_{fh}$ := ${P}^\nu_{fh}$;\\
\icc \>\hspace{2ex}\= $C$ := $C^\nu$; $M_P$ := $M^\nu_P$; $M_C$ := $M^\nu_C$;\\
\icc \>\> \If $M^\nu_P \geq M^\nu_C$ \Then $\nu := \frac{\nu}{2}$ \Else $\nu := \frac{3\nu}{2}$;\\
\icc \>\> $({P}^\nu_{f1}, \ldots, {P}^\nu_{fh}, C)$ := $\kw{BalanceP}(k,\nu)$;\\
\icc \>\> $M^\nu_P$ := $\kw{max}\{|{P}^\nu_{f1}|, \ldots, |{P}^\nu_{fh}|\}$; $M^\nu_C$ := $|C^\nu|$;\\
\icc \> \Return \{${P}_{f1}$, \ldots, ${P}_{fh}$, $C$\};
}
\vspace{-2.5ex} \myhrule
\end{center}
}
\end{center}
\vspace{-4ex}
\caption{Algorithm \kw{PFrag} \label{alg-pfrag}}
\vspace{-2ex}
\end{figure}

@@

\etitle{Correctness \& Complexity}.
The correctness is obvious as \kw{PFrag} always returns an $h$-fragmentation.
Algorithm~\kw{PFrag} runs in $O(\log h\cdot t_{\kw{BalanceP}})$, where $t_{\kw{BalanceP}}$ is the complexity of the algorithm for the {\sc $(k,\nu)$-Balanced Partition} problem. Indeed, \kw{PFrag} calls at most $\log h$ times \kw{BalanceP}, as $\nu\geq 1$.
\looseness=-1

@@

\noindent
{\textbf{1. Proof of Proposition~\ref{thm-inc-grouprec-pat}}}

@@

\noindent
{\textbf{2. Proof of Proposition~\ref{prop-fragmentation}}}

@@

@@

\vspace{-0.5ex}
The experimental results on a real-life dataset \youtube are reported here.

{\em \youtube}~\cite{youtubeWeb} contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos. We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.

\vspace{-1.8ex}
\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis, \denalk on \youtube \wrt three measurements.
The results are reported in Fig.~\ref{fig-exp-semantic-youtube-diameter} to~\ref{fig-exp-semantic-youtube-link-varyk}.
We find \optgrouprec strikes a balance at capturing the practical requirements.

>>>>

\noindent
{\textbf{1. Procedure \rgraphsim (Section~\ref{sec-tsimAlg})}}

\vspace{-2ex}
\begin{figure}[h!]
%\vspace{-2ex}
\begin{center}
{\small
\myhrule
\vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} Pattern graph $P(V_{P}, E_{P})$ and ball $\ball([v, r])$.\\
{\sl Output:\/} The perfect subgraph $G_s$ of $\ball{[v,r]}$ \wrt $P$.\\
\sstab \bcc \hspace{1ex} \= \For each $u \in V_{P}$ \Do\\
\icc \>\hspace{2ex}\= $\matchs(u)$ := \{$w | w$ is in $\ball{[v, r]}$ and $l_P(u)\in l(w)$\};\\
\icc \> \While there are changes \Do\\
\icc \>\> \For each edge ($u, u'$) in $E_P$ and each node $w \in \matchs(u)$ \Do\\
\icc \>\>\hspace{2ex}\= \If there is no edge ($w, w'$) in $\ball{[v, r]}$ with $w' \in \matchs(u')$ \Then\\
\icc \>\>\>\hspace{2ex}\= $\matchs(u)$ := $\matchs(u) \setminus \{w\}$;\\
\icc \> \If there exists $|\matchs(u)|\not\in f_{P}(u)$ \Then \Return $\emptyset$;\\
\icc \> $\Reps$ := \{$(u,w) | u \in V_{P}, w \in \matchs(u)$\};\\
\icc \> Construct the perfect subgraph $G_s$ \wrt $\Reps$;\\
\icc \> \Return $G_s$;\\
}

@@

\eat{%%EAT
\noindent
{\textbf{2. Algorithm \minp (Section~\ref{subsec-batch-opt})}}

@@

\vspace{-2ex}
\etitle{Correctness \& Complexity}. The correctness of \minp is assured by following.
(1) The maximum match relations returned by $P$ and $P_{m}$ on any data graph $G$ are always same via graph simulation.
(2) The generated capacity bound on each node in $P_{m}$ assures that, the matched nodes of $P_{m}$ in $G$ always satisfy all capacity bounds on the nodes in $P$, which are in the same equivalent class.
Till now, $P\equiv P_{m}$;
(3) For any $P'$ that $P'\equiv P_{m}$, $|P_{m}|\leq|P'|$.
Algorithm \minp is in $O(|P|^2)$ time, by the time complexity of graph simulation.
}%%%EAT

\noindent
{\textbf{3. Algorithm \kw{PFrag} (Section~\ref{sec-dynamictopk})}}

\kw{PFrag} works by connecting the {\em pattern fragmentation} problem to the
{\sc $(k, \nu)$-Balanced Partition} problem.
It is to divide the nodes of a graph into $k$ components such that each component is of size no more than $\nu\cdot\frac{|V|}{k}$, and the number of edges between different components is minimized.
As illustrated before, the $(k,\nu)$-balanced partition problem,
though is not approximable in general, has a number of sophisticated heuristic algorithms~\cite{AndreevR06}.

\vspace{-2ex}
\begin{figure}[h!]
\begin{center}
{\small
\begin{center}
\myhrule \vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} \= Pattern graph $P(V_{P},E_{P})$ and integer $h$.\\
{\sl Output:\/} An $h$-fragmentation \{${P}_{f1}$, \ldots, ${P}_{fh}$, $C$\} of $P$.\\
\sstab \bcc \hspace{0.5ex} \= $k$ := $h$; $\nu$ := $h$; $M_P$ := $|P|$; $M_C$ := 0;\\
\icc \> $({P}^\nu_{f1}, \ldots, {P}^\nu_{fh}, C^\nu)$ := $\kw{BalanceP}(k,\nu)$; \\
\icc \> $M^\nu_P$ := $\kw{max}\{|{P}^\nu_{f1}|, \ldots, |{P}^\nu_{fh}|\}$; $M^\nu_C$ := $|C^\nu|$;\\
\icc\> \While $\kw{max}\{M_P, M_C\} > \kw{max}\{M^\nu_P, M^\nu_C\}$ \Do\\
\icc \>\hspace{2ex}\= ${P}_{f1}$ := ${P}^\nu_{f1}$, \ldots, ${P}_{fh}$ := ${P}^\nu_{fh}$;\\
\icc \>\hspace{2ex}\= $C$ := $C^\nu$; $M_P$ := $M^\nu_P$; $M_C$ := $M^\nu_C$;\\
\icc \>\> \If $M^\nu_P \geq M^\nu_C$ \Then $\nu := \frac{\nu}{2}$ \Else $\nu := \frac{3\nu}{2}$;\\
\icc \>\> $({P}^\nu_{f1}, \ldots, {P}^\nu_{fh}, C)$ := $\kw{BalanceP}(k,\nu)$;\\
\icc \>\> $M^\nu_P$ := $\kw{max}\{|{P}^\nu_{f1}|, \ldots, |{P}^\nu_{fh}|\}$; $M^\nu_C$ := $|C^\nu|$;\\
\icc \> \Return \{${P}_{f1}$, \ldots, ${P}_{fh}$, $C$\};
}
\vspace{-2.5ex} \myhrule
\end{center}
}
\end{center}
\vspace{-4ex}
\caption{Algorithm \kw{PFrag} \label{alg-pfrag}}
\vspace{-2ex}
\end{figure}

@@

\vspace{-1.5ex}
\etitle{Correctness \& Complexity}.
The correctness is obvious as \kw{PFrag} always returns an $h$-fragmentation.
Algorithm~\kw{PFrag} runs in $O(\log h\cdot t_{\kw{BalanceP}})$, where $t_{\kw{BalanceP}}$ is the complexity of the algorithm for the {\sc $(k,\nu)$-Balanced Partition} problem. Indeed, \kw{PFrag} calls at most $\log h$ times \kw{BalanceP}, as $\nu\geq 1$.
\looseness=-1

@@

\noindent
{\textbf{1. Proof of Theorem~\ref{thm-tsim-radius}}}

\noindent
{\textbf{2. Proof of Proposition~\ref{thm-inc-grouprec-pat}}}

@@

\noindent
{\textbf{4. Proof of Proposition~\ref{prop-fragmentation}}}

@@

\noindent
{\textbf{5. Proof of Proposition~\ref{prop-canaffballs}}}

We will prove the proposition by contradiction.
When $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.
\identifyaffball identifies \affballsx who already match with each fragment of $P$;
Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
there must exist an update in $\Delta P$ on $P_{fi}$,
such that the ball may match with the updated fragment $P_{fi}\oplus \Delta P$.
Therefore, \identifyaffball filters out the balls that do not match with a fragment of $P$, and there are no pattern updates on the fragment.

\noindent
{\textbf{6. Proof of Proposition~\ref{prop-affected-datainc}}}

The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
\identifyaffball filters out the balls that cannot match all fragments,	and there are no data updates on the ball.

@@

\vspace{-0.5ex}

We also used another real-life dataset {\em \youtube}~\cite{youtubeWeb} for experimental verification.
It contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos. We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.

\vspace{-1.5ex}
The experimental results on \youtube are reported here.

\vspace{-1.8ex}
\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis, \denalk on \youtube \wrt four quality measures.
The results are reported in Fig.~\ref{fig-exp-semantic-youtube-diameter} to~\ref{fig-exp-semantic-youtube-link-varyk}.
We find \optgrouprec strikes a balance at capturing the practical requirements.
